Calendar-based graphics for visualising people's daily schedules

### 2017-07-19 main.Rmd
minor tweaks about abstract

---
author:
  - name: Earo Wang
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{earo.wang@monash.edu}
  - name: Dianne Cook
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{dicook@monash.edu}
  - name: Rob J Hyndman
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{rob.hyndman@monash.edu}
title:
  formatted: "Calendar-based graphics for visualising people's daily schedules"
  plain: "Calendar-based graphics for visualising people's daily schedules"
abstract: >
  We develop the \code{frame\_calendar} function that provides a method for arranging the data, which are collected at daily frequency or a time scale more frequent than daily, in a calendar-based format and accomplishes visualisation with the grammar of graphics. The calendar-based layout serves as a familiar format for the Western world and it is particularly useful to visualise people's daily schedules. One example is Melbourne pedestrian counts which are captured at hourly interval by a number of sensors. Owing to human activities, the data feature multiple temporal scales such as time of day, day of week, day of year. We describe its construction along with a few options. We provide some variations to demonstrate its usage by applying to the pedetrian data over one-year period of 2016.
keywords:
  # at least one keyword must be supplied
  formatted: [calendar-based visualisation, temporal-context data]
  plain:     [calendar-based visualisation, temporal-context data]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
  citation_package: biblatex
bibliography: ["references.bib", "packages.bib"]
---

@@

The newly computed coordinates not only work with the simple geoms such as lines and points, but also boxplot and other complex geoms. Figure \ref{fig:boxplot} uses the side-by-side boxplots with the loess smooth line superimposed as an example. It shows the distribution of hourly counts across all the 43 sensors. In general, bimodality features work days whereas unimodality features the rest of the days. The last week of December is just the holiday season: people are off work on the day before Christmas, go shopping on the Boxing day, and hanging out for the firework in the New Year Evening.

>>>>

---
author:
  - name: Earo Wang
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{earo.wang@monash.edu}
  - name: Dianne Cook
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{dicook@monash.edu}
  - name: Rob J Hyndman
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{rob.hyndman@monash.edu}
title:
  formatted: "Calendar-based graphics for visualising people's daily schedules"
  plain: "Calendar-based graphics for visualising people's daily schedules"
abstract: >
  We develop the \code{frame\_calendar} function that provides a method for arranging the data, which are collected at daily frequency or a time scale more frequent than daily, in a calendar-based format and accomplishes visualisation with the grammar of graphics. The calendar-based layout serves as a familiar format for the Western world and it is particularly useful to visualise people's daily schedules. Our motivating application is Melbourne pedestrian counts which are captured at hourly interval by a number of sensors. Owing to human activities, the data feature multiple temporal scales such as time of day, day of week, day of year. We describe its construction along with a few options. We provide some variations to demonstrate its usage by applying to the pedetrian data over one-year period of 2016.
keywords:
  # at least one keyword must be supplied
  formatted: [calendar-based visualisation, temporal-context data]
  plain:     [calendar-based visualisation, temporal-context data]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
  citation_package: biblatex
bibliography: ["references.bib", "packages.bib"]
---

@@

The newly computed coordinates not only work with the simple geoms such as lines and points, but also boxplot and other complex geoms. Figure \ref{fig:boxplot} uses the loess smooth line superimposed atop the side-by-side boxplots as an example. It shows the distribution of hourly counts across all the 43 sensors. In general, bimodality features work days whereas unimodality features the rest of the days. The last week of December is just the holiday season: people are off work on the day before Christmas, go shopping on the Boxing day, and hanging out for the firework in the New Year Evening.
